Estimating the distribution of block sizes as a function of average transaction rates

### 2017-01-17 paper/paper.tex
Added new Gamma table, old one commented out; also deleted an extraneous line from the model fitting script & removed old data file
Updated gamma fits after fixing the sql query issue
Updated the tables based on fitting the gamma process model to the end of the block chain
mode changed on a bunch of files

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 12 10:44:18 2015
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
 & Mean & 2.5\% & 97.5\% \\ 
  \hline
       $n=5000$ & 1.34 & 1.29 & 1.39 \\ 
$n=1000$, $g=1$ & 1.26 & 1.17 & 1.37 \\ 
$n=1000$, $g=2$ & 1.36 & 1.26 & 1.47 \\ 
$n=1000$, $g=3$ & 1.37 & 1.26 & 1.47 \\ 
$n=1000$, $g=4$ & 1.27 & 1.17 & 1.37 \\ 
$n=1000$, $g=5$ & 1.41 & 1.30 & 1.52 \\ 
 $n=500$, $g=1$ & 1.29 & 1.15 & 1.45 \\ 
 $n=500$, $g=2$ & 1.23 & 1.10 & 1.37 \\ 
 $n=500$, $g=3$ & 1.46 & 1.31 & 1.63 \\ 
 $n=500$, $g=4$ & 1.28 & 1.14 & 1.42 \\ 
 $n=500$, $g=5$ & 1.55 & 1.38 & 1.74 \\ 
 $n=500$, $g=6$ & 1.21 & 1.08 & 1.34 \\ 
 $n=500$, $g=7$ & 1.24 & 1.11 & 1.38 \\ 
 $n=500$, $g=8$ & 1.29 & 1.15 & 1.44 \\ 
 $n=500$, $g=9$ & 1.36 & 1.21 & 1.52 \\ 
 $n=500$, $g=10$ & 1.46 & 1.30 & 1.63 \\ 
 \hline
\end{tabular}
\caption{Posterior mean and 95\% credible intervals for $\alpha$ from fitting a gamma distribution to block sizes of the last 5000 blocks in our database. For sample sizes less than 5000, blocks were broken into groups of equal size and the model was fit separately to each group. Sample size is indicated by $n$, group id by $g$. Each model was fit in RStan \citep{rstan-software:2015,stan-software:2015} using 4 chains, each with 4000 iterations, 2000 of which used for warmup/burn in.}
\label{tab:gammafit}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 12 22:27:11 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Mean & SD & SE(Mean) & 2.5\% & 25\% & 50\% & 75\% & 97.5\% \\ 
  \hline
$\gamma$ & 0.0240 & 0.0004 & 0.0000 & 0.0232 & 0.0237 & 0.0240 & 0.0243 & 0.0248 \\ 
  $\beta$ & 15.0951 & 0.9228 & 0.0103 & 13.3725 & 14.4461 & 15.0760 & 15.6962 & 16.9591 \\ 
  $\sigma$ & 0.0024 & 0.0001 & 0.0000 & 0.0023 & 0.0023 & 0.0024 & 0.0024 & 0.0025 \\ 
   \hline
\end{tabular}
 \caption{Results of fitting the measurement error model with stochastic measurement times. We use RStan \citep{rstan-software:2015,stan-software:2015} to fit the model, obtaining four chains each of 4000 iterations, 2000 of which used for warmup/burn in.}
 \label{tab:modelfit}
\end{table}

@@

 Table \ref{tab:probsims} contains estimates of the probability of a filled block under a variety of assumptions, using parameter estimates of the posterior distribution of the model using 1000 contiguous blocks ending with block 303151. Probabilities in the first row were computed exactly using the cdf of the exponential distribution. Probabilities in the second and third rows were computed by simulating 800,000 blocks from the model at the specified values for $\gamma$ and $\beta$, where $\beta^{(0.5)}$ denotes the posterior median for $\beta$. Probabilities in the fourth row were computed by simulating 100 blocks from the model for each of the 8000 draws of from the posterior of $\beta$ and with $\gamma$ fixed at the specified values. Probabilities in the fifth and final row were computed by simulating 100 blocks for each of the 8000 draws from the posterior of $\beta$ and the shifted posterior of $\gamma$, where a draw from the shifted posterior of $\gamma$ is a draw from the posterior plus the difference between the specified $\mathrm{E}[\gamma]$ and $\gamma$'s posterior mean. 
% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Tue Oct 13 00:53:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrrrr}
  \hline
$E[\gamma] = \hat{\gamma} =$ & 0.02 & 0.03 & 0.04 & 0.05 & 0.06 & 0.07 & 0.08 & 0.09 \\ 
  \hline
$\beta = \infty$ & 0.0067 & 0.0357 & 0.0821 & 0.1353 & 0.1889 & 0.2397 & 0.2865 & 0.3292 \\ 
  $\beta = 3\times\beta^{(0.5)}$ & 0.0082 & 0.0387 & 0.0853 & 0.1383 & 0.1915 & 0.2420 & 0.2874 & 0.3293 \\ 
  $\beta = \beta^{(0.5)}$ & 0.0117 & 0.0446 & 0.0917 & 0.1435 & 0.1958 & 0.2446 & 0.2881 & 0.3300 \\ 
  $\beta \sim p(\beta|x,t)$ & 0.0119 & 0.0452 & 0.0919 & 0.1437 & 0.1954 & 0.2438 & 0.2892 & 0.3304 \\ 
  $(\beta,\gamma) \sim p(\beta,\gamma|x,t)$ & 0.0118 & 0.0448 & 0.0916 & 0.1433 & 0.1955 & 0.2442 & 0.2896 & 0.3301 \\ 
   \hline
\end{tabular}
\caption{Probability of a full block under a variety of parameter values --- $\gamma$ is the mean transaction rate and $\beta$ is a dispersion parameter so that the variance of transaction rates is $\gamma/\beta$. In the first row the transaction rate is constant at $\hat{\gamma}$, in the second through fourth rows the transaction rate is stochastic with fixed mean $\hat{\gamma}$, and in the final row the transaction rate is stochastic and unknown with mean $\hat{\gamma}$.}
\label{tab:probsims}
\end{table}

>>>>

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Wed Dec 23 10:33:41 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & Mean & 2.5\% & 97.5\% \\ 
  \hline
  $n=5000$ & 1.04 & 1.01 & 1.08 \\ 
  $n=1000$, $g=1$ & 0.93 & 0.86 & 1.00 \\ 
  $n=1000$, $g=2$ & 0.93 & 0.86 & 1.00 \\ 
  $n=1000$, $g=3$ & 1.00 & 0.92 & 1.08 \\ 
  $n=1000$, $g=4$ & 1.04 & 0.96 & 1.12 \\ 
  $n=1000$, $g=5$ & 1.52 & 1.41 & 1.64 \\ 
  $n=500$, $g=1$ & 0.89 & 0.80 & 0.99 \\ 
  $n=500$, $g=2$ & 0.97 & 0.86 & 1.08 \\ 
  $n=500$, $g=3$ & 0.92 & 0.83 & 1.02 \\ 
  $n=500$, $g=4$ & 0.94 & 0.84 & 1.04 \\ 
  $n=500$, $g=5$ & 1.26 & 1.12 & 1.40 \\ 
  $n=500$, $g=6$ & 0.83 & 0.74 & 0.92 \\ 
  $n=500$, $g=7$ & 1.04 & 0.93 & 1.16 \\ 
  $n=500$, $g=8$ & 1.04 & 0.92 & 1.15 \\ 
  $n=500$, $g=9$ & 1.40 & 1.25 & 1.57 \\ 
  $n=500$, $g=10$ & 1.67 & 1.49 & 1.86 \\ 
   \hline
\end{tabular}
\caption{Posterior mean and 95\% credible intervals for $\alpha$ from fitting a gamma distribution to block sizes of the last 5000 blocks in our database. For sample sizes less than 5000, blocks were broken into groups of equal size and the model was fit separately to each group. Sample size is indicated by $n$, group id by $g$. Each model was fit in RStan \citep{rstan-software:2015,stan-software:2015} using 4 chains, each with 4000 iterations, 2000 of which used for warmup/burn in.}
\label{tab:gammafit}
\end{table}

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Wed Dec 30 12:33:51 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & Mean & 2.5\% & 97.5\% \\ 
  \hline
  $n=5000$ & 1.04 & 1.00 & 1.07 \\ 
  $n=1000$, $g=1$ & 1.16 & 1.08 & 1.25 \\ 
  $n=1000$, $g=2$ & 1.01 & 0.93 & 1.09 \\ 
  $n=1000$, $g=3$ & 1.10 & 1.01 & 1.18 \\ 
  $n=1000$, $g=4$ & 1.00 & 0.92 & 1.08 \\ 
  $n=1000$, $g=5$ & 0.96 & 0.89 & 1.04 \\ 
  $n=500$,  $g=1$ & 1.24 & 1.11 & 1.38 \\ 
  $n=500$,  $g=2$ & 1.09 & 0.98 & 1.21 \\ 
  $n=500$,  $g=3$ & 0.98 & 0.88 & 1.09 \\ 
  $n=500$,  $g=4$ & 1.04 & 0.93 & 1.16 \\ 
  $n=500$,  $g=5$ & 1.27 & 1.13 & 1.41 \\ 
  $n=500$,  $g=6$ & 0.98 & 0.88 & 1.09 \\ 
  $n=500$,  $g=7$ & 0.92 & 0.83 & 1.02 \\ 
  $n=500$,  $g=8$ & 1.09 & 0.97 & 1.21 \\ 
  $n=500$,  $g=9$ & 1.12 & 1.00 & 1.24 \\ 
  $n=500$,  $g=10$ & 0.86 & 0.77 & 0.95 \\ 
   \hline
\end{tabular}
\caption{Posterior mean and 95\% credible intervals for $\alpha$ from fitting a gamma distribution to block sizes of the last 5000 blocks in our database. For sample sizes less than 5000, blocks were broken into groups of equal size and the model was fit separately to each group. Sample size is indicated by $n$, group id by $g$. Each model was fit in RStan \citep{rstan-software:2015,stan-software:2015} using 4 chains, each with 4000 iterations, 2000 of which used for warmup/burn in. PRE 2015}
\end{table}

% OLD TABLE
% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 12 10:44:18 2015
%% \begin{table}[ht]
%% \centering
%% \begin{tabular}{lrrr}
%%   \hline
%%  & Mean & 2.5\% & 97.5\% \\ 
%%   \hline
%%        $n=5000$ & 1.34 & 1.29 & 1.39 \\ 
%% $n=1000$, $g=1$ & 1.26 & 1.17 & 1.37 \\ 
%% $n=1000$, $g=2$ & 1.36 & 1.26 & 1.47 \\ 
%% $n=1000$, $g=3$ & 1.37 & 1.26 & 1.47 \\ 
%% $n=1000$, $g=4$ & 1.27 & 1.17 & 1.37 \\ 
%% $n=1000$, $g=5$ & 1.41 & 1.30 & 1.52 \\ 
%%  $n=500$, $g=1$ & 1.29 & 1.15 & 1.45 \\ 
%%  $n=500$, $g=2$ & 1.23 & 1.10 & 1.37 \\ 
%%  $n=500$, $g=3$ & 1.46 & 1.31 & 1.63 \\ 
%%  $n=500$, $g=4$ & 1.28 & 1.14 & 1.42 \\ 
%%  $n=500$, $g=5$ & 1.55 & 1.38 & 1.74 \\ 
%%  $n=500$, $g=6$ & 1.21 & 1.08 & 1.34 \\ 
%%  $n=500$, $g=7$ & 1.24 & 1.11 & 1.38 \\ 
%%  $n=500$, $g=8$ & 1.29 & 1.15 & 1.44 \\ 
%%  $n=500$, $g=9$ & 1.36 & 1.21 & 1.52 \\ 
%%  $n=500$, $g=10$ & 1.46 & 1.30 & 1.63 \\ 
%%  \hline
%% \end{tabular}
%% \caption{Posterior mean and 95\% credible intervals for $\alpha$ from fitting a gamma distribution to block sizes of the last 5000 blocks in our database. For sample sizes less than 5000, blocks were broken into groups of equal size and the model was fit separately to each group. Sample size is indicated by $n$, group id by $g$. Each model was fit in RStan \citep{rstan-software:2015,stan-software:2015} using 4 chains, each with 4000 iterations, 2000 of which used for warmup/burn in.}
%% \label{tab:gammafit}
%% \end{table}

@@

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Mon Dec 28 10:59:52 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Mean & SD & SE(Mean) & 2.5\% & 25\% & 50\% & 75\% & 97.5\% \\ 
  \hline
$\gamma$ & 0.0597 & 0.0012 & 0.0000 & 0.0574 & 0.0589 & 0.0597 & 0.0605 & 0.0621 \\ 
  $\beta$ & 4.4923 & 0.2382 & 0.0027 & 4.0328 & 4.3303 & 4.4866 & 4.6498 & 4.9660 \\ 
  $\sigma$ & 0.0008 & 0.0000 & 0.0000 & 0.0007 & 0.0008 & 0.0008 & 0.0008 & 0.0009 \\ 
   \hline
\end{tabular}
 \caption{Results of fitting the measurement error model with stochastic measurement times. We use RStan \citep{rstan-software:2015,stan-software:2015} to fit the model, obtaining four chains each of 4000 iterations, 2000 of which used for warmup/burn in.}
\end{table}

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Wed Dec 30 12:31:30 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Mean & SD & SE(Mean) & 2.5\% & 25\% & 50\% & 75\% & 97.5\% \\ 
  \hline
$\gamma$ & 0.0561 & 0.0009 & 0.0000 & 0.0543 & 0.0554 & 0.0561 & 0.0566 & 0.0578 \\ 
  $\beta$ & 7.0450 & 0.4327 & 0.0046 & 6.2235 & 6.7486 & 7.0402 & 7.3299 & 7.9080 \\ 
  $\sigma$ & 0.0025 & 0.0001 & 0.0000 & 0.0024 & 0.0025 & 0.0025 & 0.0026 & 0.0027 \\ 
   \hline
\end{tabular}
 \caption{Results of fitting the measurement error model with stochastic measurement times. We use RStan \citep{rstan-software:2015,stan-software:2015} to fit the model, obtaining four chains each of 4000 iterations, 2000 of which used for warmup/burn in. PRE 2015}
\end{table}

%%% OLD MODEL FITS TABLE
%% % latex table generated in R 3.2.2 by xtable 1.7-4 package
%% % Mon Oct 12 22:27:11 2015
%% \begin{table}[ht]
%% \centering
%% \begin{tabular}{rrrrrrrrr}
%%   \hline
%%  & Mean & SD & SE(Mean) & 2.5\% & 25\% & 50\% & 75\% & 97.5\% \\ 
%%   \hline
%% $\gamma$ & 0.0240 & 0.0004 & 0.0000 & 0.0232 & 0.0237 & 0.0240 & 0.0243 & 0.0248 \\ 
%%   $\beta$ & 15.0951 & 0.9228 & 0.0103 & 13.3725 & 14.4461 & 15.0760 & 15.6962 & 16.9591 \\ 
%%   $\sigma$ & 0.0024 & 0.0001 & 0.0000 & 0.0023 & 0.0023 & 0.0024 & 0.0024 & 0.0025 \\ 
%%    \hline
%% \end{tabular}
%%  \caption{Results of fitting the measurement error model with stochastic measurement times. We use RStan \citep{rstan-software:2015,stan-software:2015} to fit the model, obtaining four chains each of 4000 iterations, 2000 of which used for warmup/burn in.}
%%  \label{tab:modelfit}
%% \end{table}

@@

 Table \ref{tab:probsims} contains estimates of the probability of a filled block under a variety of assumptions, using parameter estimates of the posterior distribution of the model using 1000 contiguous blocks ending with block 303151. Probabilities in the first row were computed exactly using the cdf of the exponential distribution. Probabilities in the second and third rows were computed by simulating 800,000 blocks from the model at the specified values for $\gamma$ and $\beta$, where $\beta^{(0.5)}$ denotes the posterior median for $\beta$. Probabilities in the fourth row were computed by simulating 100 blocks from the model for each of the 8000 draws of from the posterior of $\beta$ and with $\gamma$ fixed at the specified values. Probabilities in the fifth and final row were computed by simulating 100 blocks for each of the 8000 draws from the posterior of $\beta$ and the shifted posterior of $\gamma$, where a draw from the shifted posterior of $\gamma$ is a draw from the posterior plus the difference between the specified $\mathrm{E}[\gamma]$ and $\gamma$'s posterior mean.

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Mon Dec 28 11:02:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
$E[\gamma] = \hat{\gamma} =$ & 0.02 & 0.03 & 0.04 & 0.05 & 0.06 & 0.07 & 0.08 & 0.09 \\ 
  \hline
$\beta = \infty$ & 0.0067 & 0.0357 & 0.0821 & 0.1353 & 0.1889 & 0.2397 & 0.2865 & 0.3292 \\ 
  $\beta = 3\times\beta^{(0.5)}$ & 0.0126 & 0.0462 & 0.0935 & 0.1445 & 0.1954 & 0.2445 & 0.2895 & 0.
3306 \\ 
  $\beta = \beta^{(0.5)}$ & 0.0274 & 0.0644 & 0.1102 & 0.1579 & 0.2057 & 0.2488 & 0.2911 & 0.3287 \\ 
  $\beta \sim p(\beta|x,t)$ & 0.0271 & 0.0641 & 0.1104 & 0.1582 & 0.2051 & 0.2509 & 0.2908 & 0.3290 \\ 
  $(\beta,\gamma) \sim p(\beta,\gamma|x,t)$ & 0.0271 & 0.0645 & 0.1100 & 0.1579 & 0.2058 & 0.2499 & 0.2920 & 0.3290 \\ 
   \hline
\end{tabular}
\caption{Probability of a full block under a variety of parameter values --- $\gamma$ is the mean transaction rate and $\beta$ is a dispersion parameter so that the variance of transaction rates is $\gamma/\beta$. In the first row the transaction rate is constant at $\hat{\gamma}$, in the second through fourth rows the transaction rate is stochastic with fixed mean $\hat{\gamma}$, and in the final row the transaction rate is stochastic and unknown with mean $\hat{\gamma}$.}
\end{table}

% latex table generated in R 3.2.3 by xtable 1.7-4 package
% Wed Dec 30 12:32:39 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
$E[\gamma] = \hat{\gamma} = $ & 0.02 & 0.03 & 0.04 & 0.05 & 0.06 & 0.07 & 0.08 & 0.09 \\ 
  \hline
$\beta = \infty$ & 0.0067 & 0.0357 & 0.0821 & 0.1353 & 0.1889 & 0.2397 & 0.2865 & 0.3292 \\ 
  $\beta = 3\times\beta^{(0.5)}$ & 0.0103 & 0.0423 & 0.0891 & 0.1416 & 0.1938 & 0.2440 & 0.2892 & 0.3312 \\ 
  $\beta = \beta^{(0.5)}$ & 0.0191 & 0.0549 & 0.1016 & 0.1519 & 0.2010 & 0.2478 & 0.2906 & 0.3303 \\ 
  $\beta \sim p(\beta|x,t)$ & 0.0191 & 0.0553 & 0.1014 & 0.1516 & 0.2017 & 0.2483 & 0.2907 & 0.3305 \\ 
  $(\beta,\gamma) \sim p(\beta,\gamma|x,t)$ & 0.0194 & 0.0550 & 0.1016 & 0.1517 & 0.2010 & 0.2472 & 0.2901 & 0.3310 \\ 
   \hline
\end{tabular}
\caption{Probability of a full block under a variety of parameter values --- $\gamma$ is the mean transaction rate and $\beta$ is a dispersion parameter so that the variance of transaction rates is $\gamma/\beta$. In the first row the transaction rate is constant at $\hat{\gamma}$, in the second through fourth rows the transaction rate is stochastic with fixed mean $\hat{\gamma}$, and in the final row the transaction rate is stochastic and unknown with mean $\hat{\gamma}$. PRE 2015}
\end{table}

%%%% OLD BLOCK FILL PROBABILITIES TABLE
%% % latex table generated in R 3.2.2 by xtable 1.7-4 package
%% % Tue Oct 13 00:53:54 2015
%% \begin{table}[ht]
%% \centering
%% \begin{tabular}{lrrrrrrrr}
%%   \hline
%% $E[\gamma] = \hat{\gamma} =$ & 0.02 & 0.03 & 0.04 & 0.05 & 0.06 & 0.07 & 0.08 & 0.09 \\ 
%%   \hline
%% $\beta = \infty$ & 0.0067 & 0.0357 & 0.0821 & 0.1353 & 0.1889 & 0.2397 & 0.2865 & 0.3292 \\ 
%%   $\beta = 3\times\beta^{(0.5)}$ & 0.0082 & 0.0387 & 0.0853 & 0.1383 & 0.1915 & 0.2420 & 0.2874 & 0.3293 \\ 
%%   $\beta = \beta^{(0.5)}$ & 0.0117 & 0.0446 & 0.0917 & 0.1435 & 0.1958 & 0.2446 & 0.2881 & 0.3300 \\ 
%%   $\beta \sim p(\beta|x,t)$ & 0.0119 & 0.0452 & 0.0919 & 0.1437 & 0.1954 & 0.2438 & 0.2892 & 0.3304 \\ 
%%   $(\beta,\gamma) \sim p(\beta,\gamma|x,t)$ & 0.0118 & 0.0448 & 0.0916 & 0.1433 & 0.1955 & 0.2442 & 0.2896 & 0.3301 \\ 
%%    \hline
%% \end{tabular}
%% \caption{Probability of a full block under a variety of parameter values --- $\gamma$ is the mean transaction rate and $\beta$ is a dispersion parameter so that the variance of transaction rates is $\gamma/\beta$. In the first row the transaction rate is constant at $\hat{\gamma}$, in the second through fourth rows the transaction rate is stochastic with fixed mean $\hat{\gamma}$, and in the final row the transaction rate is stochastic and unknown with mean $\hat{\gamma}$.}
%% \label{tab:probsims}
%% \end{table}
